Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-04 main.tex
Notes / polish

\iftext
Intuitively, we use the word {\em policy} for any kind of dynamic
enforcement mechanism (e.g., a runtime taint tracker, heap coloring rules,
capability hardware, etc.).
\leo{FIX: terminology}
We use {\em property} for a mathematical
predicate on programs (i.e., machine states) articulating some useful
security goal, e.g. noninterference. \iftext\bcp{Not quite true, if we stick
  with hyperproperties.} \fi
\fi

\leo{We might need to change the intuition behind some of these things.}
A {\em contour} $\contour \in \CONTOURS = \COMPONENTS \rightarrow
\{\HIGHSEC,\LOWSEC\} \times \{\HIGHINT, \LOWINT\}$\bcp{We need more mnemonic names for
  these (that help us keep straight when we're talking about confidentiality
  and when integrity) in the way they are displayed.}
is a map from machine components
to confidentiality and integrity levels. $\LOWSEC$ marks locations whose
contents are observable from the outside (by the ``attacker,'' e.g.,
by DMA) and $\HIGHSEC$ marks internal ``hidden'' state that cannot be
observed directly (e.g., processor registers and memory addresses for
temporary variables will usually be hidden). Similarly, $\LOWINT$
locations correspond to low-integrity components (e.g. locations that
can be written to \bcp{directly or indirectly} by the network), while $\HIGHINT$ locations should be
protected from such flows.

@@

\bcp{A random thought about integrity: One thing that may be helping confuse
  us about integrity is that we've gone back and forth between ``eager'' and
  ``lazy'' versions of various micropolicies, where the ``lazy'' ones do
  allow high-integrity data to be overwritten, but only in a way that it
  cannot be read again later (e.g., the lazy heap policy guarantees that, if
  inaccessible memory is overwritten, then its color will change).  The lazy
point of view is much more subtle as an integrity property.  So, to keep our
heads straight here, we should be thinking only about eager properties in
the first instance.}

@@

Let $\initmach$ be the set of initial states of the machine and let
$\initcontour(M)$ be the initial contour assigned to each $M \in
\initmach$.\leo{This could probably be generalized to a set}

For each $M \in \initmach$ and $C = \initcontour(M)$, we define the
{\em closure} of $(C,M)$ as the set of triples of (contour, trace,
trace) as follows:
\[
\begin{array}{rcl}
  \closure{(C,M)} = \{ ( C_i, \seq{N}, \seq{N'})
  & | & C_{i-1} \not = C_i \\
  & , & \seq{(C_i, M_i)} = \induced{C}{M}\\
  & , & \seq{(\_, N_j)} = \induced{C_i}{M_i}\\
  & , & N'_0 \in \variant{C_i}{M_i}\\
  & , & \seq{(\_, N'_j)} = \induced{C_i}{N_0'} \}\\
\end{array}  
\]
\leo{Alternative: We could do this for all $i$, but lose the
  trivial instantiation of noninterference later on}

@@

A pair of traces $\seq{M}$ and $\seq{N}$ satisfy the {\em
  confidentiality} safety hyperproperty with respect to a contour
$\contour$, if, if the initials states are variants $N_0 \in
\variant{C}{M_0}$, then their observations coincide
$\obstrace(\contour, \seq{M}) = \obstrace(\contour, \seq{N})$.
\leo{Should we cut at minimum length for termination-insensitiveness?}

@@

@@

\begin{itemize}
\item
How does Nick’s stack policy actually work these days?
\item Andrew remembers that Catalin looked at something like this a long time ago and they decided that they needed unique tags for each dynamic call, not just levels.  We should check.
\end{itemize}

>>>>

\iftext
Intuitively, we use the word {\em policy} for any kind of dynamic
enforcement mechanism (e.g., a runtime taint tracker, heap coloring rules,
capability hardware, etc.).
We use {\em property} for a mathematical
condition on programs (i.e., machine states) articulating some useful
security goal, e.g. noninterference.
\fi

\leo{We might need to change the intuition behind some of these things.}
A {\em contour} $\contour \in \CONTOURS = \COMPONENTS \rightarrow
\{\HIGHSEC,\LOWSEC\} \times \{\HIGHINT, \LOWINT\}$\bcp{We need more mnemonic names for
  these (that help us keep straight when we're talking about confidentiality
  and when integrity) in the way they are displayed.}
is a map from machine components
to confidentiality and integrity levels. $\LOWSEC$ marks locations whose
contents are observable from the outside (by the ``attacker,'' e.g.,
by DMA) and $\HIGHSEC$ marks internal ``hidden'' state that cannot be
observed directly (e.g., processor registers and memory addresses for
temporary variables will usually be hidden). Similarly, $\LOWINT$
locations correspond to low-integrity components (e.g. locations that
can be written to \iftext \bcp{directly or indirectly} \fi by the network), while $\HIGHINT$ locations should be
protected from such flows.

@@

@@

Let $\initmach$ be the set of initial states of the machine and let
$\initcontour(M)$ be the\bcp{an?} initial contour assigned to each $M \in
\initmach$. \iftext\leo{This could probably be generalized to a set}\fi

For each $M \in \initmach$ and $C = \initcontour(M)$, we define the
{\em closure} of $(C,M)$ as the set of triples of (contour, trace,
trace) as follows:
\[
\begin{array}{rcl}
  \closure{(C,M)} = \{ ( C_i, \seq{N}, \seq{N'})
  & | & C_{i-1} \not = C_i \\
  & , & \seq{(C_i, M_i)} = \induced{C}{M}\\
  & , & \seq{(\_, N_j)} = \induced{C_i}{M_i}\\
  & , & N'_0 \in \variant{C_i}{M_i}\\
  & , & \seq{(\_, N'_j)} = \induced{C_i}{N_0'} \}\\
\end{array}
\]
\leo{Alternative: We could do this for all $i$, but lose the
  trivial instantiation of noninterference later on}
\bcp{Don't follow the notation here.  :-(}

@@

A pair of traces $\seq{M}$ and $\seq{N}$ satisfy the {\em
  confidentiality} safety hyperproperty with respect to a contour
$\contour$, if, if the initials states are variants $N_0 \in
\variant{C}{M_0}$, then their observations coincide:
$\obstrace(\contour, \seq{M}) = \obstrace(\contour, \seq{N})$.
\leo{Should we cut at minimum length for termination-insensitiveness?}
\bcp{Or just ask that one be a prefix of the other?}

@@

\begin{itemize}
\item
How does Nick’s stack policy actually work these days?
\item Andrew remembers that Catalin looked at something like this a long time ago and they decided that they needed unique tags for each dynamic call, not just levels.  We should check.
\item \bcp{A random thought about integrity: One thing that may be helping confuse
  us about integrity is that we've gone back and forth between ``eager'' and
  ``lazy'' versions of various micropolicies, where the ``lazy'' ones do
  allow high-integrity data to be overwritten, but only in a way that it
  cannot be read again later (e.g., the lazy heap policy guarantees that, if
  inaccessible memory is overwritten, then its color will change).  The lazy
point of view is much more subtle as an integrity property.  So, to keep our
heads straight here, we should be thinking only about eager properties in
the first instance.}
\end{itemize}

@@
